---
title: "Homework 5"
author: Danyang Gui
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```





```{r, error = TRUE}
city_prop_test = function(df) {
  
  n_unsovled ...
  n_total ... 
  
  prop.test(.....)
  
}
homicide_df = 
  read_csv("data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") %>% 
  nest(data = resolved)
```





## Problem 2


import one dataset 

```{r}
path_df = 
  tibble(
    path = list.files("lda_data"),
  ) %>% 
  mutate(
    path = str_c("lda_data/", path),
    data = map(path, read_csv)) %>%
  unnest(data)
```


tidy the dataset:


```{r}
lda_df = 
  path_df %>%
  mutate(
    subject_id = str_replace(path, ".csv", ""),
    subject_id = str_replace(subject_id, "lda_data/", "")) %>%
 select(subject_id, week_1:week_8) %>%
 separate(subject_id, into = c("group", "id"), sep = "_") %>%
 pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observed_value",
  ) %>%
  mutate(
    group = case_when(
      group == "con" ~ "Control_arm",
      group == "exp" ~ "Experimental_arm"))

lda_df
```



make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
plot =
  lda_df %>%
  unite(subject_id, group, id) %>% 
  ggplot(aes(x = week, y = observed_value, group = subject_id, color = subject_id)) +
  geom_point() +
  geom_line()

plot
```

From the spaghetti plot, we can tell that the subjects in the two groups have similar values at the beginning of the study. During the 8 weeks of observation, the subjects in the experimental arm collectively have a higher measurements than subjects in the control arm. 


## Problem 3

```{r}
t_esti_pvalue = function(n = 30, mu, sigma = 5) { #default sample size and sd
  
  sim_data =
    tibble(
     x = rnorm(n, mean = mu, sd = sigma)
    )
  
  sim_data %>%
    summarize(
      t_test = t.test(x, mu = mu, conf.level = 0.95) %>% 
        broom::tidy() %>% 
        select(p.value, estimate)
  )
  
}
```



```{r}
set.seed(100)
sim_results_0 =   
  rerun(5000, t_esti_pvalue(mu = 0)) %>% 
  bind_rows() %>% 
  mutate(
    mu_hat = pull(t_test,estimate),
    p_value = pull(t_test,p.value)) %>% 
  select(-t_test)

sim_results_0
```




```{r}
set.seed(100)
results_df = 
  tibble(mu_value = c(0,1,2,3,4,5,6)) %>% 
  mutate(
    output_lists = map(.x = mu_value, ~rerun(5000, t_esti_pvalue(mu = .x))),
    estimate_pvalue_df = map(output_lists, bind_rows)) %>%
  select(-output_lists) %>%
  unnest(estimate_pvalue_df) %>%
  mutate(
    mu_hat = t_test$estimate,
    p_value = t_test$p.value) %>% 
  select(mu_value, mu_hat, p_value)


results_df

```




Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of mu on the x axis. Describe the association between effect size and power.

```{r}
plot_1 = 
  results_df %>%
  group_by(mu_value) %>% 
  filter(p_value < 0.05) %>% 
  count() %>% 
  mutate(
    proportion = n / 5000
  ) %>% 
  ggplot(aes(x = mu_value, y = proportion, color = mu_value)) +
  geom_point()+
  geom_line() +
  labs(
    title = "The power of the t.test versus the true value of mu",
    x = "True value of mu",
    y = "The proportion when the null hypothesis is rejected") + 
  scale_x_continuous(
    breaks = c(0,1,2,3,4,5,6), 
    limits = c(0,6)) 

plot_1
```

The power increases as the effect size(true value of mu) increases.




Make a plot showing the average estimate of mu on the y axis and the true value of mu on the x axis.

```{r}
plot_2 =
  results_df %>%
  group_by(mu_value) %>% 
  summarize(
    average_estimate = mean(mu_hat)
  ) %>% 
  ggplot(aes(x = mu_value, y = average_estimate, color = mu_value)) +
  geom_point()+
  geom_line() +
  labs(
    title = "The average estimate of mu hat versus true value of mu",
    x = "True value of mu",
    y = "The average estimate of mu hat") + 
  scale_x_continuous(
    breaks = c(0,1,2,3,4,5,6), 
    limits = c(0,6)) 

plot_2
```

